Hybrid platforms and bargaining power

### 2023-03-24 src/paper/application.tex
Slightly rewrite entry and equilibrium section

\newtheorem{proposition}{Proposition}
\newtheorem{corollary}{Corollary}
\newtheorem{lemma}{Lemma}
\newtheorem{assumption}{Assumption}
\crefname{assumption}{assumption}{assumptions}

@@

                \node[anchor=north west] at (axis cs: .1, .9) {Fringe ($A$)};
                \node[anchor=south east] at (axis cs: .9, .1) {Player $P$};
            \end{axis}
        \end{tikzpicture}
        \caption{Fringe firms are substitutes}
    \end{subfigure}
    \caption{Distribution of value between player $P$ and the fringe}
    \label{fig:outcome_based_bargaining_power}
\end{figure}

@@

The equilibrium number of entrants is determined by a free entry condition: in the end, the fringe firms' profits should be equal to the investment cost.
\begin{assumption}
    \label{ass:free_entry}
    In equilibrium, $\pi_F(N_P, N_F) = I_F N_F$.
\end{assumption}

In order to guarantee a unique equilibrium, let us make the following, additional assumption about the profit and bargaining weight functions.
\begin{assumption}
    \label{ass:single_crossing}
    Let $f$ and $w$ be such that the following holds for all $N_F, N_P \geq 0$:
    \begin{gather*}
        f'_{n_F} (N_P, N_F) < \int_0^1 s w(s) f'_{n_F} (N_P, s N_F) \ds \\
        \text{or} \\
        f''_{n_F} (N_P, N_F) < \int_0^1 s^2 w(s) f''_{n_F} (N_P, s N_F) \ds.
    \end{gather*}
\end{assumption}
\textcolor{red}{TODO: Find interpretable sufficient conditions for this assumption.}

>>>>

\newtheorem{definition}{Definition}
\newtheorem{proposition}{Proposition}
\newtheorem{corollary}{Corollary}
\newtheorem{lemma}{Lemma}
\newtheorem{assumption}{Assumption}
\crefname{assumption}{assumption}{assumptions}

@@

                \node[anchor=north west] at (axis cs: .1, .9) {Fringe ($A$)};
                \node[anchor=south east] at (axis cs: .9, .1) {Player $P$};
            \end{axis}
        \end{tikzpicture}
        \caption{Fringe firms are substitutes}
    \end{subfigure}
    \caption{Distribution of value between the platform and the fringe (with $w(s) \equiv 1$)}
    \label{fig:outcome_based_bargaining_power}
\end{figure}

@@

The equilibrium number of entrants is determined by a free entry condition: in the end, the fringe firms' profits should be equal to the investment cost.
\begin{definition}
    \label{ass:free_entry}
    Let us define a free entry equilibrium by the following conditions:
    \begin{itemize}
        \item Profits are shared according to \cref{ass:profit_sharing}.
        \item Entrants make zero profits: $\pi_F(N_P, N_F) = I_F N_F$ after accounting for entry costs.
    \end{itemize}
\end{definition}

Finally, in order to guarantee a unique equilibrium, let us make the following, an additional assumption about the profit and bargaining weight functions.
\begin{assumption}
    \label{ass:single_crossing}
    Let $f$ and $w$ be such that the following holds for all $N_F, N_P \geq 0$:
    \begin{gather*}
        f'_{n_F} (N_P, N_F) < \int_0^1 s w(s) f'_{n_F} (N_P, s N_F) \ds \\
        \text{or} \\
        f''_{n_F} (N_P, N_F) < \int_0^1 s^2 w(s) f''_{n_F} (N_P, s N_F) \ds.
    \end{gather*}
\end{assumption}
The above assumption essentially guarantees that the profit of the fringe (as a function of the number of entrants) has at most a single crossing with the total entry cost (apart from the obvious $N_F=0$ intersection).
While the conditions is not very simple to interpret, they can be verified once a specific choice for $f$ and $w$ is made.
In particular, this assumption will be satisfied in the example in \cref{sec:example}.
